\begin{frame}{\glsentrydesc{es}s}%{Definition}
    % \begin{itemize}
    %     \item An embedded system is a dedicated computer system designed to perform one or a few dedicated functions, often in real-time.
    %     \item Unlike general-purpose computers, embedded systems have specific tasks.% and do not look like computers.
    % \end{itemize}
    \par An embedded system is a dedicated computer system designed to perform one or a few dedicated functions, often in real-time.
    \par Unlike general-purpose computers, embedded systems have specific tasks.
%\end{frame}

%\begin{frame}{\glsentrydesc{es}s}%{Components}
    \begin{itemize}
        \item \textbf{Microcontroller}\newline The \acl{cpu} of the system, includes integrated memory.
        \item \textbf{\acs{io} Devices}\newline Interact with the external world (e.g., sensors, actuators).
        \item \textbf{Software}\newline Program instructions that control the system.
    \end{itemize}
\end{frame}

\begin{frame}{\glsentrydesc{es}s}{Examples}
    \begin{itemize}
        \item \textbf{Home Appliances}\newline Microwave ovens, washing machines, and thermostats.
        \item \textbf{Automotive Controls}\newline Anti-lock braking systems, airbag systems, and fuel injection controls.
        \item \textbf{Industrial Automation}\newline Programmable logic controllers (PLCs), digital signal processors, and assembly line robots.
        \item \textbf{Consumer Electronics}\newline Smartphones, smart watches, and fitness trackers.
    \end{itemize}
\end{frame}

\begin{frame}{\glsentrydesc{es}s}{Characteristics}
    \begin{itemize}
        \item \textbf{Real-Time Operation}\newline Many embedded systems operate in real-time, meaning they respond to inputs or events without delay\footnote{In real-time systems, tasks have to be completed within certain time constraints. A delay in task completion could lead to undesired outcomes or system failures.}.
        \item \textbf{Dedicated Functions}\newline They are designed to execute specific tasks.
        \item \textbf{Long Lifecycle}\newline Embedded systems usually have a long lifecycle and may not require updates as frequently as general-purpose computers.
        \item \textbf{Resource Constraints}\newline Often operate with limited memory and processing power.
    \end{itemize}
\end{frame}